Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing

### 2018-05-02 paper.tex
Updates to paper

\[\Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}\]

\[\overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}\]

In terms of angles:

@@

\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
[Bartelmann 2001]

\[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
    \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
\right)\]

In terms of angles:

@@

@@

@@

\subsection{Current plan}
\begin{itemize}
    \item Calculate tangential shear and deflection angle for NFW and SIS
    \item Consider single foreground lens halo with many background galaxies
    \item How to arrange and distribute background halos?
    \begin{itemize}
        \item Initial ellipticity
        \item angular density on sky
        \item sizes
    \end{itemize}
    \item Apply shear and deflection angle to background galaxies
    \item Attempt to fit both profiles, subtracting intrinsic shear, see if the fit is distinguishable
    \item How many foreground halos to test? - start with 1
    \item What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift

\end{itemize}

Fake data:
N sets of e1, e2, theta1, theta2

Analyzing data:
make histogram in annulus
mean and standard deviation
use log bins for theta

50 gals/square arcminute
5 arcminutes
$z_L = 0.3$
$z_S = 1$
$M_{halo} = 10^15$ solar masses
instrinsic ellipticity from gaussian with width 0.2

Assume same DS since this can be determined by redshift anyway

estimating ellipticity has well-documented issues [cite] due to noise and PSF

>>>>

% \[\Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}\]
%
% \[\overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}\]
% 
% In terms of angles:

@@

% \[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
%
%
% \[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
%     \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
% \right)\]
%
% In terms of angles:

@@

Similar convention used by \citet{Bartelmann2001}

@@

Estimating ellipticity has well-documented issues [cite] due to noise and PSF

\newpage

@@

\begin{enumerate}
    \item Calculate tangential shear and deflection angle for NFW and cored isothermal profiles.
    \item Consider single foreground lens halo with many background galaxies.
    \begin{itemize}
        \item Start with one NFW halo, then maybe consider more tests.
    \end{itemize}
    \item Construct background galaxies:
    \begin{itemize}
        \item Number density on sky: 50 galaxies/square arcminute
        \item Intrinsic ellipticity drawn from Gaussian distribution with $\mu=0, \sigma=0.2$
        \item Assume they are all that the same distance $D_S$ since this can be determined by redshift (neglecting some noise)
    \end{itemize}
    \item Recommended values:
    \begin{itemize}
        \item $z_L = 0.3$
        \item $z_S = 1.0$
        \item $M_{halo} = 10^{15} M_\odot$
    \end{itemize}
    \item Apply shear and deflection angle to background galaxies, get fake data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
    \item Bin galaxies in annuli by $\theta$ value (use log bins for theta)
    \item Calculate mean and standard deviation of ellipticity
    \item Attempt to fit both NFW and isothermal profiles, see if the fit is distinguishable
\end{enumerate}

\subsection{Questions}
\begin{itemize}
    \item How to properly do sigma contours?
    \item What theta range should we look at? (5 arcminutes?)
    \item What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift - can we use current time?
    \item Using $c = 10$?
    \item Where to go from here?
\end{itemize}

\section{Results}
